%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.1, 21 November 2016) written by
% LianTze Lim (liantze@gmail.com), based on the 
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you want to use \orcid or the
%% academicons icons, add "academicons"
%% to the \documentclass options. 
%% Then compile with XeLaTeX or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}
\documentclass[10pt,a4paper]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% When using the "academicons" option,
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font %% folder.


% Change the page layout if you need to
\geometry{left=1cm,right=7.0cm,marginparwidth=6cm,marginparsep=0.5cm,top=1cm, bottom=0cm}


% Change the font if you want to.

% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{fancyhdr}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{VividRed}{HTML}{C43D3C}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{black}{HTML}{000000}
\definecolor{soSleepy}{HTML}{EBE7E0}
\definecolor{darkBejeweled}{HTML}{322740}
\definecolor{bejeweled}{HTML}{5E1E43}
\definecolor{pink}{HTML}{9E1C48}

\colorlet{heading}{black}
\colorlet{accentBright}{pink}
\colorlet{background}{soSleepy}
\colorlet{subtitle1}{darkBejeweled}
\colorlet{subtitle2}{bejeweled}
\colorlet{subtitle3}{pink}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}


\begin{document}
\name{Ashley Martinez}
\tagline{}

% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{ashley.carrasquel@gmail.com}
  \phone{786-537-3822}
  \location{Miami, FL}
  \linkedin{linkedin.com/in/ashleymartinezcarrasquel}
  \break 
  \begin{quote}
    \newline 
Bilingual technical product manager and full-stack engineer with a passion for user experience and quality tech. Proven track record of guiding \newline teams through the software development life cycle to create user-centric solutions that generate positive business results.
  \end{quote}
}

%% Make the header extend all the way to the right, if you want. Extend the right margin by 8cm (=6.8cm marginparwidth + 1.2cm marginparsep)
\begin{adjustwidth}{}{-8cm}
\makecvheader
\end{adjustwidth}

\cvsection[page1sidebar]{Professional Experience}
\cvevent{Smilestack LLC}{Founder}{Miami, FL}{03/2024 – Present}
\begin{itemize}
\item Created many processes to operate my own consulting and real estate business.
\item Introduced Kanban agile methodology for JV Construction Group that enabled better management of the construction of a new store for luxury retailer, CONCEPTS. The system delighted stakeholders as we created a road map that clarified timelines. I coached management through the organizational change process.
\item Modernized the brand of local restaurant Fresh \& Wild Fish using AI.

\end{itemize}
\divider

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvevent{CVS Health}{Technical Product Manager}{Remote}{06/2022 – 11/2023}
\begin{itemize}
\item Incorporating human-centered design by working with 3 Specialty Pharmacy IT teams of 20+ engineers.  
\item Lead critical modernization efforts to replace mainframe repricing of multi-million dollar rebate programs.
\item Discovered solution that would not alter tight deadlines after identifying key gaps in road map of product and bringing together key players to solve. 
\item Responsible for product road map. Reduced risk to timelines by informing of roadblocks and team needs in a timely manner, making difficult hiring decisions, and procuring additional resources to bolster team.
\item Lead a team of 5 engineers and 2 designers in scrum ceremonies and team building activities to create a culture of collaboration and high performance.
\end{itemize}
\divider

\cveventTitleWithDates{J.P. Morgan Chase \& Co}{06/2017 - 06/2022}
\cveventSubTeam{Software Engineer}{Jersey, NJ}{UI Frameworks Team}
\begin{itemize}
\item Built and took to production a new application that provides real-time information to treasurers across industry using
 \textit{React Typescript, Java, and Springboot}. 
\item Collaborated with product owners and fellow engineers to implement stable and reusable components across the stack - including building proxies, APIs, and feature rich React web apps.
\item Designed several features using Figma based on UX research I conducted.
\item Modernized a legacy application by migrating to Typescript, resulting in faster debugging and output from engineers on the team.
\item Configured CI/CD Jenkins pipeline that automated deployment scripts resulting in improved code quality.
\end{itemize}
\vspace{5pt}
\cveventSubTeam{Software Engineer}{New York, NY}{Trade Compliance Team}
\begin{itemize}
\item  Designed and implemented in-house analytical tools to support compliance teams.
\item Productionized feature that visualizes Bloomberg daily news feeds using \textit{Java, Javascript, and several data modeling exercises in Oracle SQL}.
\item Configured CI/CD Jenkins pipeline that automated deployment scripts resulting in improved code quality. 
\end{itemize}
\vspace{5pt}
\cveventSubTeam{Software Engineering Program - Steering Committee Lead}{}{}
\begin{itemize}
\item Lead several hiring and retention efforts within the firm in a leadership role, including speaking publicly at large town hall meetings and community events.
\end{itemize}
\end{document}
